---
title: "Untitled"
author: "Qingyue Su"
date: "11/13/2019"
output: html_document
---

```{r}
library(sandwich)
library(plm)
library(lmtest)
library(stargazer)
library(tidyverse)
library(knitr)
library(car)
library(readr)
library(dplyr)
library(readxl)
library(zoo)
library(carData)
library(data.table)
```

### Question1

#### Import Data
```{r}
# Import Data Set 1
CPSC_Enrollment <- read.csv("data/CPSC_Enrollment_Info_2019_10.csv")
#View(CPSC_Enrollment)
head(CPSC_Enrollment)
```

```{r}
# Import Data Set 2
Monthly_Report <- read.csv("data/Monthly_Report_By_Plan_2019_10.csv")
#View(Monthly_Report)
head(Monthly_Report)
```

```{r}
# Import Data Set 3
MajorInsuranceOrgs <- read_excel("data/MajorInsuranceOrgs.xlsx")
#View(MajorInsuranceOrgs)
head(MajorInsuranceOrgs)
```

```{r}
# Import Data Set 4
PBP_Benefits_2020_dictionary <- read_excel("data/PBP-Benefits-2020-Q1/PBP_Benefits_2020_dictionary.xlsx")
#View(PBP_Benefits_2020_dictionary)  
head(PBP_Benefits_2020_dictionary)
```

```{r}
# Import Data Set 5
pbp_b16_dental <- read.delim("data/PBP-Benefits-2020-Q1/pbp_b16_dental.txt")
#View(pbp_b16_dental)
head(pbp_b16_dental)
```

```{r}
#read the excel extract from "MA HEDIS Public Use Files 2018",we only need sheet EOC 170, and we use the column
#'EOC170-0010',we then delete all the NAs in the file and read it
uod <- read_excel('data/uod.xlsx')
#View(uod)
head(uod)
```

#### Data Description & Data Cleaning

##### Data Set 1
```{r}
unique(CPSC_Enrollment['Enrollment'])
```

```{r}
CPSC_Enrollment_1 <- CPSC_Enrollment %>% filter(Enrollment != "*" & State %in% c("NY","MI","TN","MN","OK","NV","ID","DE","WY"))

head(CPSC_Enrollment_1)
```

```{r}
unique(CPSC_Enrollment_1$Contract.Number)
```

```{r}
unique(substr(CPSC_Enrollment_1$Contract.Number,1,1))
```

```{r}
CPSC_Enrollment_new <- CPSC_Enrollment_1 %>% filter(substr(CPSC_Enrollment_1$Contract.Number,1,1) != "S")

head(CPSC_Enrollment_new)
```

##### Data Set 2

```{r}
Monthly_Report_1 <- Monthly_Report %>% filter(Enrollment != "*")
Monthly_Report_new <- Monthly_Report_1 %>% filter(substr(Monthly_Report_1$Contract.Number,1,1) != "S")
#View(Monthly_Report_new)
head(Monthly_Report_new)
```

##### Data Set 3

```{r}
#merge majorname
merge_majorname <- merge(Monthly_Report_new, MajorInsuranceOrgs, by.x = "Organization.Marketing.Name", by.y = "Organization Marketing Name")
#View(merge_majorname)
head(merge_majorname)
```

```{r}
#merje contract.name
merge_majorname_id_name <- distinct(merge_majorname[,c("Contract.Number","MajorInsuranceOrgName")])
#View(merge_majorname_id_name)

merge_contract_new <- merge(merge_majorname_id_name, CPSC_Enrollment_new, by = "Contract.Number")
#View(merge_contract_new)
head(merge_contract_new)
```

```{r}
#transfrom the format
merge_contract_new$Enrollment <- as.numeric(as.character(merge_contract_new$Enrollment))

#write.csv(merge_contract_new, file = "data/merge_contract_new.csv")
head(merge_contract_new)
```

```{r}
#sum state
sumstate <- merge_contract_new %>% group_by(State) %>% summarise(sum_state = sum(Enrollment))
#View(sumstate)
head(sumstate)
```

```{r}
#sum state & company
sumstate_company <- merge_contract_new %>% group_by(State, MajorInsuranceOrgName) %>% summarise(sumstate_company = sum(Enrollment))
#View(sumstate_company)
head(sumstate_company)
```

```{r}
#merge state & company
merge_state_company <- merge(sumstate, sumstate_company, by = "State")
#View(merge_state_company)
head(merge_state_company)
```

```{r}
merge_state_company$market_share <- round(merge_state_company$sumstate_company / merge_state_company$sum_state,4)
merge_state_company <- merge_state_company %>% arrange(State, -market_share)
#View(merge_state_company)
#write.csv(merge_state_company, file = "data/merge_state_company.csv",  sep = "", row.names = FALSE, col.names = TRUE)
head(merge_state_company)
```

```{r}
# HHI = (Xi/X)^2
# In these 4 companies, the market share of them are respectily 40%, 25%, 17% and 18%, so the HHI is equal to 0.2838, whose calculation process is shown below.
# HHI= 0.4^2 + 0.25^2 + 0.17^2 + 0.18^2= 0.2838
HHI <- merge_state_company %>% group_by(State) %>% summarise(HHI = sum(market_share^2)) %>% arrange(-HHI)
#View(HHI)
head(HHI, 5)
```

```{r}
# select the highest market share among these six states seperately
state_group <- group_by(merge_state_company, State)
state_group_new <- summarise(state_group, max_market_share = max(market_share))
#View(state_group_new)
head(state_group_new)
```

```{r}
# select top five highest market share among these six states seperately
merge_state_company_top5 <- merge_state_company %>% group_by(State) %>% mutate(row = row_number()) %>% 
  filter(row <= 5)
#View(merge_state_company_top5)
head(merge_state_company_top5)
```

### Question2

```{r}
#find useful column
pbp_b16_dental_new <- pbp_b16_dental[,c("pbp_a_hnumber","pbp_a_plan_identifier","segment_id","pbp_b16a_bendesc_yn","pbp_b16b_bendesc_yn")]
#View(pbp_b16_dental_new)
head(pbp_b16_dental_new)
```

```{r}
pbp_b16_dental_new_row <- pbp_b16_dental_new %>%
  group_by(pbp_a_hnumber,pbp_a_plan_identifier) %>% 
  arrange(pbp_a_hnumber, pbp_a_plan_identifier, segment_id) %>%
  mutate(row = row_number()) %>%
  filter(row <= 1)
#View(pbp_b16_dental_new_row)
head(pbp_b16_dental_new_row)
```

```{r}
pbp_b16_dental_new <- pbp_b16_dental_new_row
head(pbp_b16_dental_new)
```

```{r}
#merge contract and plan
pbp_b16_dental_new$pbp_a_plan_identifier <- as.factor(pbp_b16_dental_new$pbp_a_plan_identifier)
#View(pbp_b16_dental_new)

merge_contract_new$Plan.ID <- as.factor(merge_contract_new$Plan.ID)
#View(merge_contract_new)

merge_contract_plan <- merge(merge_contract_new, pbp_b16_dental_new, by.x = c("Contract.Number","Plan.ID"), by.y = c("pbp_a_hnumber","pbp_a_plan_identifier"))
#View(merge_contract_plan)

head(merge_contract_plan)
```

```{r}
#merge contract_plan with top-5
merge_contract_plan_top5 <- merge(merge_state_company_top5, merge_contract_plan, by = c("State", "MajorInsuranceOrgName"))
#View(merge_contract_plan_top5)
head(merge_contract_plan_top5)
```

```{r}
#a What percentages of the enrollees enjoy the “Preventive Dental Items as a supplemental benefit under Part C”?
Pre_Dental <- merge_contract_plan_top5 %>% filter(pbp_b16a_bendesc_yn==1) %>% group_by(State,MajorInsuranceOrgName) %>% summarise(sum_pre_dental = sum(Enrollment))
#View(Pre_Dental)

Total <- merge_contract_plan_top5 %>% group_by(State,MajorInsuranceOrgName) %>% summarise(sum_total = sum(Enrollment))
#View(Total)

merge_pre_dental <- merge(Pre_Dental, Total, by = c("State","MajorInsuranceOrgName"))
merge_pre_dental$percentages_of_preventive_dental <- round(merge_pre_dental$sum_pre_dental/merge_pre_dental$sum_total,4)
merge_pre_dental <- merge_pre_dental %>% arrange(State, -percentages_of_preventive_dental)
#View(merge_pre_dental)

head(merge_pre_dental)
```

```{r}
#b What percentages of the enrollees enjoy the “Comprehensive Dental Items as a supplemental benefit under Part C”?
Com_Dental <- merge_contract_plan_top5 %>% filter(pbp_b16b_bendesc_yn==1) %>% group_by(State,MajorInsuranceOrgName) %>% summarise(sum_com_dental = sum(Enrollment))
#View(Com_Dental)

merge_com_dental <- merge(Com_Dental, Total, by = c("State","MajorInsuranceOrgName"))
merge_com_dental$percentages_of_comprehensive_dental <- round(merge_com_dental$sum_com_dental/merge_com_dental$sum_total,4)
merge_com_dental <- merge_com_dental %>% arrange(State, -percentages_of_comprehensive_dental)
#View(merge_com_dental)

head(merge_com_dental)
```

### Question3
```{r}
head(merge_contract_new)
```


```{r}
contract <- merge_contract_new[,c("Contract.Number","MajorInsuranceOrgName","Plan.ID","State","Enrollment")]
head(contract)
```

```{r}
head(uod)
```

```{r}
colnames(uod)[2] = 'uod_rate'
head(uod)
```

```{r}
#mearge the two table together to get the uod of each contract, then we change the data type
uodstate=merge(contract,uod,by.x='Contract.Number',by.y='Contract Number')
uodstate$Enrollment = as.numeric(uodstate$Enrollment)
uodstate$uod_rate = as.numeric(uodstate$uod_rate)

head(uodstate)
```

```{r}
glimpse(uodstate)
```

In the following steps, I filtered the table by the states one by one and get the weighted calculated uod rate for each contract,

Then I grouped them by the top 10 company, order from highest udo rate to lowest.

However, in fact, some state doesn't have 10 companies, or some top 10 companies do not have uod rate, so I just included all the data, which means that some states may have company numbers less than 10.


```{r}
contract = data.table(contract)
uod = data.table(uod)
uodstate = data.table(uodstate)
```

```{r}
#NY
uodny = uodstate[State=='NY']
uodny[,totalenrollment:=sum(Enrollment),by=Contract.Number ]
uodny1=uodny[,{tmp1=Enrollment*uod_rate; tmp2=tmp1/totalenrollment; tmp3=sum(tmp2); list(uod_company=tmp3)}, 
             by=MajorInsuranceOrgName]

head(uodny1)
```

```{r}
head(merge_state_company)
```

```{r}
company_share = data.table(merge_state_company)
```

```{r}
#combine with company market share to get the top 10 companies in NY before ordering by UOD rate.
order_company = merge(x = uodny1, y = company_share, by = "MajorInsuranceOrgName", all.x = TRUE)
order_ny = order_company[State =='NY'][order(market_share, decreasing = TRUE)][1:10]
uodny2 = order_ny[order(uod_company,decreasing=TRUE)]
#fwrite(uodny2, "UOD of NY states.csv")

head(uodny2)
```

```{r}
#MI
uodmi = uodstate[State=='MI']
uodmi[,totalenrollment:=sum(Enrollment),by=Contract.Number ]
uodmi1=uodmi[,{tmp1=Enrollment*uod_rate; tmp2=tmp1/totalenrollment; tmp3=sum(tmp2); list(uod_company=tmp3)}, 
             by=MajorInsuranceOrgName]
uodmi2 = uodmi1[order(uod_company,decreasing=TRUE)][1:10]
#fwrite(uodmi2, "UOD of MI states(1).csv")

head(uodmi2)
```

```{r}
#TN
uodtn = uodstate[State=='TN']
uodtn[,totalenrollment:=sum(Enrollment),by=Contract.Number ]
uodtn1=uodtn[,{tmp1=Enrollment*uod_rate; tmp2=tmp1/totalenrollment; tmp3=sum(tmp2); list(uod_company=tmp3)}, by=MajorInsuranceOrgName]
uodtn2 = uodtn1[order(uod_company,decreasing=TRUE)][1:10]
#fwrite(uodtn2, "UOD of TN states.csv")

head(uodtn2)
```

```{r}
#MN
uodmn = uodstate[State=='MN']
uodmn[,totalenrollment:=sum(Enrollment),by=Contract.Number ]
uodmn1=uodmn[,{tmp1=Enrollment*uod_rate; tmp2=tmp1/totalenrollment; tmp3=sum(tmp2); list(uod_company=tmp3)}, by=MajorInsuranceOrgName]
uodmn2 = uodmn1[order(uod_company,decreasing=TRUE)][1:10]
#fwrite(uodmn2, "UOD of MN states.csv")

head(uodmn2)
```

```{r}
#OK
uodok = uodstate[State=='OK']
uodok[,totalenrollment:=sum(Enrollment),by=Contract.Number ]
uodok1=uodok[,{tmp1=Enrollment*uod_rate; tmp2=tmp1/totalenrollment; tmp3=sum(tmp2); list(uod_company=tmp3)}, by=MajorInsuranceOrgName]
uodok2 = uodok1[order(uod_company,decreasing=TRUE)]
#fwrite(uodok2, "UOD of OK states.csv")

head(uodok2)
```

```{r}
#NV
uodnv = uodstate[State=='NV']
uodnv[,totalenrollment:=sum(Enrollment),by=Contract.Number ]
uodnv1=uodnv[,{tmp1=Enrollment*uod_rate; tmp2=tmp1/totalenrollment; tmp3=sum(tmp2); list(uod_company=tmp3)}, by=MajorInsuranceOrgName]
uodnv2 = uodnv1[order(uod_company,decreasing=TRUE)]
#fwrite(uodnv2, "UOD of NV states.csv")

head(uodnv2)
```

```{r}
#ID
uodid = uodstate[State=='ID']
uodid[,totalenrollment:=sum(Enrollment),by=Contract.Number ]
uodid1=uodid[,{tmp1=Enrollment*uod_rate; tmp2=tmp1/totalenrollment; tmp3=sum(tmp2); list(uod_company=tmp3)}, by=MajorInsuranceOrgName]
uodid2 = uodid1[order(uod_company,decreasing=TRUE)]
#fwrite(uodid2, "UOD of ID states.csv")

head(uodid2)
```

```{r}
#DE
uodde = uodstate[State=='DE']
uodde[,totalenrollment:=sum(Enrollment),by=Contract.Number ]
uodde1=uodde[,{tmp1=Enrollment*uod_rate; tmp2=tmp1/totalenrollment; tmp3=sum(tmp2); list(uod_company=tmp3)}, by=MajorInsuranceOrgName]
uodde2 = uodde1[order(uod_company,decreasing=TRUE)]
#fwrite(uodde2, "UOD of DE states.csv")

head(uodde2)
```

```{r}
#WY
uodwy = uodstate[State=='WY']
uodwy[,totalenrollment:=sum(Enrollment),by=Contract.Number ]
uodwy1=uodwy[,{tmp1=Enrollment*uod_rate; tmp2=tmp1/totalenrollment; tmp3=sum(tmp2); list(uod_company=tmp3)}, by=MajorInsuranceOrgName]
uodwy2 = uodwy1[order(uod_company,decreasing=TRUE)]
#fwrite(uodwy2, "UOD of WY states.csv")

head(uodwy2)
```
